---
title: "MIIN Part 4: Meta-dataset overview"
author: "Marissa Lee"
date: "June 1, 2015"
output: pdf_document
---

**Filename: MIIN_4_datasetOverview.Rmd**  
**This markdown file does the following tasks:**
1. Article selection statistics  

2. Number of papers and observations  

3. Types of observations  

4. Plant species statistics 

5. Cover data statistics

6. Trait data statistics  

7. Soil measurement statistics  

8. Effect size statistics  

9. CWM trait value statistics  

```{r libraries, echo=TRUE}
knitr::opts_chunk$set(cache=TRUE)

citation()
library(plyr)
if(nchar(system.file(package="plyr"))) citation("plyr")
library(doBy)
library(ggplot2)
if(nchar(system.file(package="ggplot2"))) citation("ggplot2")
library(reshape2)
library(gridExtra)
library(metafor)
if(nchar(system.file(package="metafor"))) citation("metafor")

source('CODE/mytheme.R')

figuresPath<-file.path(getwd()[1], "FIGURES_TABLES", "overview") #where to put the saved plots
fig.height<-2.5 #inches
fig.width<- 2.5 #inches
fig.res<-300

#from MIIN_3_calcEffectSizes.Rmd
papers<-read.table("DATA/DATA_SYNTHESIZED/calcES/papers.txt", sep="\t") 
observations<-read.table("DATA/DATA_SYNTHESIZED/calcES/observations.txt", header=TRUE, sep="\t") 
cover<-read.table("DATA/DATA_SYNTHESIZED/calcES/cover.txt", header=TRUE, sep="\t") 
species<-read.table("DATA/DATA_SYNTHESIZED/calcES/species.txt", header=TRUE, sep="\t") 
traits<-read.table("DATA/DATA_SYNTHESIZED/calcES/traits.txt", header=TRUE, sep="\t") 
measures<-read.table("DATA/DATA_SYNTHESIZED/calcES/measures.txt", header=TRUE, sep="\t")
cwm<-read.table("DATA/DATA_SYNTHESIZED/calcES/cwm.txt", header=TRUE, sep="\t")
spIDcover<-read.table("DATA/DATA_SYNTHESIZED/calcES/spIDcover.txt", header=TRUE, sep="\t")
spIDtraits<-read.table("DATA/DATA_SYNTHESIZED/calcES/spIDtraits.txt", header=TRUE, sep="\t")
metaDataset<-read.table("DATA/DATA_SYNTHESIZED/calcES/metaDataset.txt", header=TRUE, sep="\t")
```

_________________________________________________________________
# 1. Article selection statistics
```{r articleSelect,echo=TRUE, warning=FALSE, message=FALSE}
### Number of papers detected by source ###
summ.papers <- ddply(papers,~source,summarise,
                     numPapers=length(read), 
                     numAcceptedPapers=sum(reject=='No'))
summ.papers<-orderBy(~-numPapers, summ.papers)
summ.papers

### Number of unique number of papers detected ###
summ.papers2 <- ddply(papers,~source+rejectRationale,summarise,
                     numPapers=length(read), 
                     numAcceptedPapers=sum(reject=='No'))
summ.papers2<-orderBy(~-numPapers, summ.papers2)
totalNumReturned<-sum(summ.papers$numPapers) #total number of papers detected
numAlreadyFound<-sum(summ.papers2[summ.papers2$rejectRationale == 'alreadyFound' & !is.na(summ.papers2$rejectRationale),'numPapers']) #number of repeat papers
numUnique<-totalNumReturned - numAlreadyFound #total number of unique papers detected
paste(numUnique, 'unique papers identified by search criteria and their references')
paste(sum(summ.papers$numAcceptedPapers), 'papers were accepted')
length(unique(metaDataset$paperID)) #this should be the same number

### Subset papers detected by the previous meta-analysis, Liao2007 ###
papers$source2<-'New studies'
papers[papers$source=='Liao2007','source2']<-'Liao 2008'
papers$reject<-revalue(papers$reject, c("No"="Accepted papers", "Yes"="Rejected papers"))

#plot number of papers that were accepted/rejected from Liao 2008 and this search
pHist_papers<-ggplot(papers, aes(x=year, fill=source2)) + mytheme + 
  facet_wrap(~reject, scales="free_y", ncol=1) + 
  geom_histogram() +  scale_y_continuous(expand = c(0,0)) +
  ylab('Count') + xlab('Year') +
  scale_fill_manual(values=c('gray','black'))
pHist_papers
newfilename<-"pHist_papers.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*1.5, height = fig.height*2, res=fig.res)
pHist_papers
dev.off()

#what was the year of the most recent data included in Liao 2008?
maxLiaoyr<-max(papers[papers$source == 'Liao2007','year'])
paste(maxLiaoyr, 'was the most recent year that data was included in the Liao 2008 meta-analysis')

#how many accepted papers were published after the most recent Liao 2008 reference?  
accepted.after<-subset(papers, source != 'Liao2007' & reject == 'Accepted papers' & year > maxLiaoyr)
paste(dim(accepted.after)[1], 'papers were accepted after the most recent reference included in Liao 2008')

#how many papers were rejected that were referenced in Liao 2008? Remember that Liao 2008 also addressed the impact of invasion on soil C pools and fluxes.
rejected.Liao<-subset(papers, source == 'Liao2007' & reject == 'Rejected papers')
numLiaoRej<-dim(rejected.Liao)[1]
all.Liao<-subset(papers, source == 'Liao2007')
numLiaoAll<-dim(all.Liao)[1]
paste(dim(rejected.Liao)[1], 'papers that were used in Liao 2008 were rejected from this study, or', round((numLiaoRej/numLiaoAll) *100, digits=2), '% of Liao references')

#How many papers were accepted that were published before the most recent Liao 2008 reference and were not included in the Liao 2008 references. 
accepted.before<-subset(papers, source != 'Liao2007' & reject == 'Accepted papers' & year < maxLiaoyr)
numAccBef<-dim(accepted.before)[1]
paste(dim(accepted.before)[1], 'papers that were published before the most recent Liao 2008 reference were included in this meta-analysis, but overlooked by Liao 2008')

#attached the 'source2' column to the metaDataset
temp_indx<-papers[,c('paperID','source2')]
metaDataset<-merge(metaDataset, temp_indx, by='paperID')

#re-write the metaDataset file so that it has the source2 column
newfilename<-'metaDataset.txt'
synthdataPath<-file.path(getwd()[1], "DATA", "DATA_SYNTHESIZED", "calcES")
write.table(metaDataset, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')
```
  
_________________________________________________________________
# 2. Number of papers and observations
```{r papersObs,echo=TRUE, warning=FALSE, message=FALSE}
#how many observations?
paste(length(unique(observations$obsID)), 'observations in the full dataset')
length(unique(metaDataset$obsID)) #these should be the same

#how many observations per paper?
summ.obs <- ddply(observations,~paperID,summarise, numObs=length(paperID))
median(summ.obs$numObs); range(summ.obs$numObs)
pHist_obs<-ggplot(summ.obs, aes(x=numObs)) + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) +
  geom_histogram() + mytheme + 
  ylab('Count') + xlab('Number of observations per paper')
pHist_obs
```

_________________________________________________________________
# 3. Types of observations
```{r obsTypes,echo=TRUE, warning=FALSE, message=FALSE}
summ.obs.eco <- ddply(observations,~ecosystCat,summarise, numObs=length(paperID))
summ.obs.st <- ddply(observations,~studyType,summarise, numObs=length(paperID))
summ.obs.nfix <- ddply(observations,~Nfix,summarise, numObs=length(paperID))
factorlist<-list(summ.obs.eco, summ.obs.st, summ.obs.nfix)
factortab<-ldply(factorlist)
factortab$factor<-c(rep('ecosystem',5), rep('studyType', 4), rep('Nfix',4))
factortab$level<-NA
factortab[!is.na(factortab$ecosystCat),'level']<-as.character(factortab[!is.na(factortab$ecosystCat),'ecosystCat'])
factortab[!is.na(factortab$studyType),'level']<-as.character(factortab[!is.na(factortab$studyType),'studyType'])
factortab[!is.na(factortab$Nfix),'level']<-as.character(factortab[!is.na(factortab$Nfix),'Nfix'])
factortab1<-factortab[,c('factor','level','numObs')]
factortab1

newfilename<-'numObsTable.txt'
write.table(factortab1, file=paste(figuresPath,newfilename, sep='/'), sep='\t') 
```  

_________________________________________________________________
# 4. Plant species statistics 
What is the distribution of invasive species per observation?  Native species? Are certain invasive species over-represented?  
```{r spp,echo=TRUE, warning=FALSE, message=FALSE}
#what is the distribution of invasive species per observation?
summ.spp <- ddply(species,~obsID,summarise, 
                  numTotalspp=length(obsID), 
                  numInvspp=sum(spInvasive=='invasive' & spExotic=='exotic' & spFocal=='focal'), 
                  numNonInvspp=sum(spInvasive=='not invasive'),
                  numOthers=numTotalspp-(numInvspp + numNonInvspp))
hist_Inv<-ggplot(summ.spp, aes(x=numInvspp)) + geom_histogram() + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) + 
  mytheme +  
  ylab('Count') + xlab('Number of invasive species per observation')
hist_Inv; median(summ.spp$numInvspp); range(summ.spp$numInvspp)

hist_Nat<-ggplot(summ.spp, aes(x=numNonInvspp)) + geom_histogram() + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) +  
  mytheme +  
  ylab('Count') + xlab('Number of non-invasive species per observation')
hist_Nat; median(summ.spp$numNonInvspp); range(summ.spp$numNonInvspp)

#number of observations per species
summ.spp.nam <- ddply(species,~spName+spFocal+spExotic,summarise, 
                  numObs=length(obsID), 
                  numPapers=length(unique(paperID)))
spp.many<-summ.spp.nam[which(summ.spp.nam$numObs > 9 & summ.spp.nam$spFocal == 'focal'),] #more than 9 observations
spp.many.o<-orderBy(~-numObs, spp.many)
spp.many.o
positions<-spp.many.o$spName
pHist_spp<-ggplot(spp.many.o, aes(x=spName, y=numObs)) + geom_bar(stat='identity') + 
  scale_y_continuous(expand=c(0,0)) + scale_x_discrete(limits = positions) +
  mytheme +  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  ylab('Number of observations') + xlab('Invasive species')
pHist_spp
newfilename<-'pHist_spp.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*2, height = fig.height*2, res=fig.res)
pHist_spp
dev.off()

#which species appear both as exotic and native species in the dataset? 
summ.spp <- ddply(species,~spName+spExotic, summarise, 
                  numObs=length(obsID),
                  numPapers=length(unique(paperID)))
summ.spp.nam2 <- ddply(summ.spp,~spName,summarise, 
                  numInvNat=length(spExotic)) 
summ.spp.nam2[summ.spp.nam2$numInvNat==2,] # if the length of spInvasive col==2, then there is native and invasive listed
```  

_________________________________________________________________
# 5. Cover data statistics
What percent of observations have measured cover data? 
```{r cover,echo=TRUE, warning=FALSE, message=FALSE}
summ.cov.obs <- ddply(cover,~obsID,summarise, 
                  numMeasured= sum(covQuality=='measured'))
numMeasured.obs<-sum(summ.cov.obs$numMeasured > 0) #number of observations with cover measurement values
numtotal.obs<-length(summ.cov.obs$numMeasured > 0) #total number of observations
cov.obs.perc<-round((numMeasured.obs / (numtotal.obs) ) *100, digits=2)
paste(cov.obs.perc, '% of observations have any cover data at all that was measured in the original paper',collapse='')

#What is the frequency of cover observations for each cover measure type? 
summ.cov <- ddply(cover,~covCat,summarise, 
                  numMeas = length(obsID),
                  numObs=length(unique(obsID)), 
                  numPapers=length(unique(paperID)))
orderBy(~-numMeas, summ.cov)

#What units are commonly reported for each cover measure type?
summ.covUnit <- ddply(cover,~covCat+covUnit,summarise, 
                      numMeas = length(obsID),
                      numObs=length(unique(obsID)), 
                      numPapers=length(unique(paperID)))
COVCAT<-unique(summ.covUnit$covCat)
covUnitList<-list()
i<-0
for(i in 1:length(COVCAT)){
  subdf<-summ.covUnit[summ.covUnit$covCat==COVCAT[i],]
  covUnitList[[as.character(COVCAT[i])]]<-orderBy(~-numMeas, subdf)
}
covUnitList

#A more detailed look at cover data quality as it contributes to CWM values...
cwm.calc<-subset(cwm, qualityCWMcalc == 'calculated')
summ.cwm <- ddply(cwm.calc,~traitCat+invType,summarise,
                  numObs=length(unique(obsID)),
                  num1spAll_1=sum(qualityCover=='Measured=All, 1sp=All'),
                  num1spAll_2=sum(qualityCover=='Measured=None, 1sp=All'),
                  num1spAll_3=sum(qualityCover=='Measured=NA, 1sp=NA'),
                  num1spAll_4=sum(qualityCover=='Measured=Mid, 1sp=All'),
                  totalspAll=sum(num1spAll_1, num1spAll_2, num1spAll_3, num1spAll_4),
                  perc1spAll=(totalspAll/numObs) *100,
                  percEqual=100-perc1spAll)
summ.cwm #cover data quality by traitCat and invType
summ.cwm2 <- ddply(summ.cwm,~invType,summarise,
                  mean1sp=mean(perc1spAll),
                  meanEqual=mean(percEqual),
                  seEqual=sd(percEqual)/sqrt(length(percEqual)))
summ.cwm2 #aggregated across traitCat

summ.cwm3 <- ddply(cwm,~invType+traitCat+obsID,summarise,
                  numReported=sum(qualityCWMcalc=='reported'))
summ.cwm4 <- ddply(summ.cwm3,~traitCat+invType,summarise,
                  count=sum(numReported != 0),
                  total=length(obsID),
                  percCWMReported=(count/total)*100)
summ.cwm4 #percent of CWM data that was reported in the original paper (rather than calculated based on species cover and trait database values)
```  

_________________________________________________________________
# 6. Trait data statistics
```{r traits,echo=TRUE, warning=FALSE, message=FALSE}
# what percent of observations had trait data reported within the original article?
n.ot<-length(unique(traits$obsID)) # number of observations with trait data
n.o<-length(unique(observations$obsID)) # total number of observations
tr.obs.perc<-round((n.ot/n.o) *100, digits=2) # percent of observations with trait data
paste(tr.obs.perc, '% of observations with species-level trait data from the original paper',collapse='')

summ.tr <- ddply(traits,~traitCat,summarise, 
                 numObs = length(unique(obsID)), 
                 numPapers = length(unique(paperID)))
summ.tr.o<-orderBy(~-numObs, summ.tr)
summ.tr.o
positions<-summ.tr.o$traitCat
pBar.tr<-ggplot(summ.tr.o, aes(x=traitCat, y=numObs)) + geom_bar(stat='identity') + 
  scale_y_continuous(expand=c(0,0)) + 
  scale_x_discrete(limits = positions, 
                   labels = c("sp_percN" = "Leaf %N",
                              "sp_cn" = "Leaf C:N", 
                              "sp_litterpercN" = "Litter %N",
                              "sp_littercn" = "Litter C:N")) +
  mytheme +  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  ylab('Number of observations') + xlab('Trait type (species-level)')

#What units and methods are commonly reported for each measurement? 
summ.traitUnit <- ddply(traits,~traitCat+traitUnit,summarise, 
                   numMeas = length(obsID),
                   numObs=length(unique(obsID)), 
                   numPapers=length(unique(paperID)))
summ.traitUnit
TRAITCAT<-unique(summ.traitUnit$traitCat)
traitUnitList<-list()
i<-0
for(i in 1:length(TRAITCAT)){
  subdf<-summ.traitUnit[summ.traitUnit$traitCat==TRAITCAT[i],]
  traitUnitList[[as.character(TRAITCAT[i])]]<-orderBy(~-numMeas, subdf)
}
traitUnitList
```  

_________________________________________________________________
# 7. Soil measurement statistics
```{r meas,echo=TRUE, warning=FALSE, message=FALSE}
summ.meas <- ddply(measures,~measCat,summarise, numObs=length(unique(obsID)))
summ.meas.o<-orderBy(~-numObs, summ.meas)
summ.meas.o

#What units and methods are commonly reported for each measurement?  
summ.measUnit <- ddply(measures,~measCat+unit,summarise, 
                   numMeas = length(obsID),
                   numObs=length(unique(obsID)))
MEASCAT<-unique(summ.measUnit$measCat)
measUnitList<-list()
i<-0
for(i in 1:length(MEASCAT)){
  subdf<-summ.measUnit[summ.measUnit$measCat==MEASCAT[i],]
  measUnitList[[as.character(MEASCAT[i])]]<-orderBy(~-numMeas, subdf)
}
measUnitList

#re-order measCat levels
metaDataset$measCat <- factor(metaDataset$measCat, levels = measCat_order)

#re-shape measures so that inv and nat are in the same column temporarily
tmp<-ddply(metaDataset, ~obsID+measCat, summarize,
      m1i_logt = unique(m1i_logt),
      m2i_logt = unique(m2i_logt),
      measQuality = unique(measQuality))
tmp$obsID<-as.factor(tmp$obsID)
m.tmp<-melt(tmp, idcols=c('obsID','measCat','measQuality'))
m.tmp$invType<-rep(NA,length(dim(m.tmp)[1])) 
m.tmp[m.tmp$variable == 'm1i_logt','invType']<-'inv'
m.tmp[m.tmp$variable == 'm2i_logt','invType']<-'ref'

#Shapiro Test
# ddply(measures, ~measCat, summarise, 
#       shapTest=shapiro.test(value)$p.value,
#       shapTest.Ln=shapiro.test(log(value+1))$p.value)
#none are normal according to Shapiro test

# Q-Q plots
qq<-ggplot(m.tmp, aes(sample=value)) + 
  facet_wrap(~measCat, scales='free', ncol=3) +
  stat_qq() + mytheme + ggtitle('QQ Plots of \nstd. measurement values')
qq
newfilename<-"qq_meas.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
qq
dev.off()


# Plot Quality Histograms
#re-order measQuality levels
m.tmp$measQuality <- factor(m.tmp$measQuality, levels = c('NoAgg.NoConv','NoAgg.Conv','Agg.NoConv','Agg.Conv'))

pHist_measQual<-ggplot(data=m.tmp, aes(x=value,fill=measQuality)) + mytheme +
  facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  scale_y_continuous(expand = c(0,0)) + 
  scale_fill_manual(name = "Quality",
                    labels = c("Agg.Conv"="Aggregated & Converted", 
                               "Agg.NoConv"="Aggregated",
                               "NoAgg.Conv"="Converted",
                               "NoAgg.NoConv"="None"),
                    values=c("Agg.Conv" = "purple",
                             "Agg.NoConv" = "red",
                             "NoAgg.Conv" = "blue",
                             "NoAgg.NoConv" = "black")) +
  ylab('Count') + xlab('Standardized measurement value')
pHist_measQual
newfilename<-"pHist_measQual.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3.5, height = fig.height*6, res=fig.res)
pHist_measQual
dev.off()
```  

_________________________________________________________________
# 8. Effect size statistics
```{r ESmeas,echo=TRUE, warning=FALSE, message=FALSE}
#re-shape measures so that inv and nat are in the same column temporarily
tmp<-ddply(metaDataset, ~obsID+measCat, summarize,
      yi = unique(yi),
      measQuality = unique(measQuality))
tmp$obsID<-as.factor(tmp$obsID)

#Shapiro Test
# ddply(measures, ~measCat, summarise, 
#       shapTest=shapiro.test(value)$p.value,
#       shapTest.Ln=shapiro.test(log(value+1))$p.value)
#none are normal according to Shapiro test

# Q-Q plots
qq<-ggplot(tmp, aes(sample=yi)) + 
  facet_wrap(~measCat, scales='free', ncol=3) +
  stat_qq() + mytheme + ggtitle('QQ Plots of \nstd. measurement values')
qq
newfilename<-"qq_ESmeas.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
qq
dev.off()

#Plot Quality Histograms
#re-order measQuality levels
tmp$measQuality <- factor(tmp$measQuality, levels = c('NoAgg.NoConv','NoAgg.Conv','Agg.NoConv','Agg.Conv'))

pHist_ESmeasQual<-ggplot(data=tmp, aes(x=yi,fill=measQuality)) + mytheme +
  facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  scale_y_continuous(expand = c(0,0)) + 
  scale_fill_manual(name = "Quality",
                    labels = c("Agg.Conv"="Aggregated & Converted", 
                               "Agg.NoConv"="Aggregated",
                               "NoAgg.Conv"="Converted",
                               "NoAgg.NoConv"="None"),
                    values=c("Agg.Conv" = "purple",
                             "Agg.NoConv" = "red",
                             "NoAgg.Conv" = "blue",
                             "NoAgg.NoConv" = "black")) +
  ylab('Count') + xlab('Standardized measurement value')
pHist_ESmeasQual
newfilename<-"pHist_ESmeasQual.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3.5, height = fig.height*6, res=fig.res)
pHist_measQual
dev.off()
```  

_________________________________________________________________
# 9. CWM trait value statistics
```{r cwm,echo=TRUE, warning=FALSE, message=FALSE}
#re-order measCat levels
metaDataset$traitCat <- factor(metaDataset$traitCat, levels = traitCat_order)
#re-shape measures so that inv and nat are in the same column temporarily
tmp<-ddply(metaDataset, ~obsID+traitCat, summarize,
      InvArea_cwm = unique(InvArea_cwm),
      InvSpInvArea_cwm = unique(InvSpInvArea_cwm),
      NatArea_cwm = unique(NatArea_cwm),
      CWMDiff_cwm = unique(CWMDiff_cwm),
      InvArea_qualRank = unique(InvArea_qualRank),
      InvSpInvArea_qualRank = unique(InvSpInvArea_qualRank),
      NatArea_qualRank = unique(NatArea_qualRank),
      CWMDiff_qualRank = unique(InvArea_qualRank)+ unique(NatArea_qualRank))

tmp$obsID<-as.factor(tmp$obsID)
m.tmp<-melt(tmp, idcols=c('obsID','traitCat'))
m.tmp$dataType<-rep(NA,length(dim(m.tmp)[1])) #dataType
m.tmp[grepl('_qualRank', m.tmp$variable),'dataType']<-'qualRank'
m.tmp[grepl('_cwm', m.tmp$variable),'dataType']<-'cwm'
m.tmp$invType<-rep(NA,length(dim(m.tmp)[1])) #invType
m.tmp[grepl('InvArea', m.tmp$variable),'invType']<-'InvArea'
m.tmp[grepl('InvSpInvArea', m.tmp$variable),'invType']<-'InvSpInvArea'
m.tmp[grepl('NatArea', m.tmp$variable),'invType']<-'NatArea'
m.tmp[grepl('CWMDiff', m.tmp$variable),'invType']<-'CWMDiff'
c.tmp<-dcast(m.tmp, obsID+traitCat+invType~dataType)
c.tmp<-c.tmp[!is.na(c.tmp$cwm),]

# #Shapiro Test
# ddply(cwm, ~traitCat, summarise, 
#       shapTest=shapiro.test(cwm)$p.value,
#       shapTestLn=shapiro.test(log10(cwm))$p.value)
# #none are normal according to Shapiro test

# Q-Q plots
qq<-ggplot(c.tmp, aes(sample=cwm)) + 
  facet_wrap(~traitCat+invType, scales='free', ncol=4) + 
  stat_qq() + mytheme + ggtitle('QQ Plots of \n cwm trait values')
qq
newfilename<-"qq_cwm.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*4, height = fig.height*3, res=fig.res)
qq
dev.off()


#Plot Factor Histograms
#InvType
cwm$obsID<-as.factor(cwm$obsID)
cwm$n_invSp_invArea<-as.factor(cwm$n_invSp_invArea)
cwm$n_invSp_natArea<-as.factor(cwm$n_invSp_natArea)
cwm$n_natSp_invArea<-as.factor(cwm$n_natSp_invArea)
cwm$n_natSp_natArea<-as.factor(cwm$n_natSp_natArea)

#Nfix
cwm.tmp<-merge(cwm, observations, by='obsID')

#plot
cwm.tmp.cn<-subset(cwm.tmp, traitCat %in% c('cn','littercn'))
pHist_cwm_cn<-ggplot(data=cwm.tmp.cn, aes(x=cwm,fill=Nfix)) + 
  facet_wrap(~invType+traitCat, scales='fixed',ncol=2) + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) +
  geom_histogram() + mytheme +
  ylab('Count') + xlab('CWM trait value')
pHist_cwm_cn
newfilename<-"pHist_cwm_cn.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*2.5, height = fig.height*3, res=fig.res)
pHist_cwm_cn
dev.off()

cwm.tmp.percn<-subset(cwm.tmp, traitCat %in% c('percN','litterpercN'))
pHist_cwm_percn<-ggplot(data=cwm.tmp.percn, aes(x=cwm,fill=Nfix)) + 
  facet_wrap(~invType+traitCat, scales='fixed',ncol=2) + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) +
  geom_histogram() + mytheme +
  ylab('Count') + xlab('CWM trait value')
pHist_cwm_percn
newfilename<-"pHist_cwm_percn.png"
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*2.5, height = fig.height*3, res=fig.res)
pHist_cwm_percn
dev.off()
```  
