---
title: "MIIN Part 4: Meta-dataset overview"
author: "Marissa Lee"
date: "June 1, 2015"
output: pdf_document
---

**Filename: MIIN_4_datasetOverview.Rmd**  
**This markdown file does the following tasks:**
1. Article selection statistics  

2. Number of papers and observations  

3. Types of observations  

4. Plant species statistics 

5. Cover data statistics

6. Trait data statistics  

7. Soil measurement statistics  

8. Effect size statistics  

9. CWM trait value statistics  

```{r libraries, echo=TRUE}
#knitr::opts_chunk$set(cache=TRUE)

require(plyr)
require(doBy)
require(ggplot2)
require(reshape2)
require(gridExtra)
require(metafor)

source('CODE/mytheme.R')

figuresPath<-file.path(getwd()[1], "FIGURES_TABLES", "overview") #where to put the saved plots
fig.height<-2.5 #inches
fig.width<- 2.5 #inches
fig.res<-300

#from MIIN_3_calcEffectSizes.Rmd
papers<-read.table("DATA/DATA_SYNTHESIZED/calcES/papers.txt", sep="\t") 
vilaRefs<-read.table("DATA/Vila_references.txt", header=TRUE, sep="\t")
castroRefs<-read.table("DATA/CastroDiez_references.txt", header=TRUE, sep="\t")
observations<-read.table("DATA/DATA_SYNTHESIZED/calcES/observations.txt", header=TRUE, sep="\t") 
cover<-read.table("DATA/DATA_SYNTHESIZED/calcES/cover.txt", header=TRUE, sep="\t") 
species<-read.table("DATA/DATA_SYNTHESIZED/calcES/species.txt", header=TRUE, sep="\t") 
traits<-read.table("DATA/DATA_SYNTHESIZED/calcES/traits.txt", header=TRUE, sep="\t") 
measures<-read.table("DATA/DATA_SYNTHESIZED/calcES/measures.txt", header=TRUE, sep="\t")
cwm<-read.table("DATA/DATA_SYNTHESIZED/calcES/cwm.txt", header=TRUE, sep="\t")
cwm.quality<-read.table("DATA/DATA_SYNTHESIZED/calcES/cwm_quality.txt", header=TRUE, sep="\t")
spIDcover<-read.table("DATA/DATA_SYNTHESIZED/calcES/spIDcover.txt", header=TRUE, sep="\t")
spIDtraits<-read.table("DATA/DATA_SYNTHESIZED/calcES/spIDtraits.txt", header=TRUE, sep="\t")
numberOfSpecies.cwm<-read.table("DATA/DATA_SYNTHESIZED/calcES/numberOfSpecies_cwms.txt", header=TRUE, sep="\t")
metaDataset<-read.table("DATA/DATA_SYNTHESIZED/calcES/metaDataset.txt", header=TRUE, sep="\t")
```

_________________________________________________________________
# 1. Article selection statistics
```{r articleSelect,echo=TRUE, warning=FALSE, message=FALSE}
### Number of papers detected by source ###
summ.papers <- ddply(papers,~source,summarise,
                     numPapers=length(read), 
                     numAcceptedPapers=sum(reject=='No'))
summ.papers<-orderBy(~-numPapers, summ.papers)
summ.papers

### Number of unique number of papers detected ###
summ.papers2 <- ddply(papers,~source+rejectRationale,summarise,
                     numPapers=length(read), 
                     numAcceptedPapers=sum(reject=='No'))
summ.papers2<-orderBy(~-numPapers, summ.papers2)
totalNumReturned<-sum(summ.papers$numPapers) #total number of papers detected
numAlreadyFound<-sum(summ.papers2[summ.papers2$rejectRationale == 'alreadyFound' & !is.na(summ.papers2$rejectRationale),'numPapers']) #number of repeat papers
numUnique<-totalNumReturned - numAlreadyFound #total number of unique papers detected
paste(numUnique, 'unique papers identified by search criteria and their references')
paste(sum(summ.papers$numAcceptedPapers), 'papers were accepted')
length(unique(metaDataset$paperID)) #this should be the same number

### Identify which papers were also detected by Vila 2011 and Castro-Diez 2014
papers.a<-papers[papers$reject == 'No',]
dim(papers.a)
length(unique(papers.a$paperID))

#vila
vilaRefs1<-vilaRefs[,2:3]
colnames(vilaRefs1)<-c('author1','year')
vilaRefs1$vila<-rep('Yes',dim(vilaRefs1)[1])
papers.a.tmp<-merge(papers.a, vilaRefs1, all.x=TRUE)

#problem: merge added rows without different info
dim(papers.a.tmp) #there are extra rows in here
length(unique(papers.a.tmp$paperID)) #same number of unique paperIDs
# tmp<-ddply(papers.a.tmp, ~paperID, summarise,
#            nRows=length(author1))
# tmp[tmp$nRows>1,]
# papers.a.tmp[papers.a.tmp$paperID %in% c(78,715),] # I have no idea why this happened
#solution: pull out unique rows
papers.a.new<-ddply(papers.a.tmp, ~paperID, summarise,
           nRows=length(author1),
           author1.new=unique(author1),
           year.new=unique(year),
           title.new=unique(title),
           journal.new=unique(journal),
           source.new=unique(source),
           vila.new=unique(vila))
#papers.a.new

#castro-diez
castroRefs1<-castroRefs[,2:3]
colnames(castroRefs1)<-c('author1.new','year.new')
castroRefs1$castroDiez<-rep('Yes',dim(castroRefs1)[1])
papers.a.tmp1<-merge(papers.a.new, castroRefs1, all.x=TRUE)

#problem: merge added rows without different info
dim(papers.a.tmp1) #there are extra rows in here
length(unique(papers.a.tmp1$paperID)) #same number of unique paperIDs
#solution: pull out unique rows
papers.a.new1<-ddply(papers.a.tmp1, ~paperID, summarise,
           author1=unique(author1.new),
           year=unique(year.new),
           title=unique(title.new),
           journal=unique(journal.new),
           source=unique(source.new),
           vila=unique(vila.new),
           castroDiez.new=unique(castroDiez))
#papers.a.new1

#liao
papers.a.new1[papers.a.new1$source == 'Liao2007','liao']<-'Yes'
#View(papers.a.new1)
colnames(papers.a.new1)[colnames(papers.a.new1)=='castroDiez.new']<-'castroDiez'
papers.a<-papers.a.new1[,c('paperID','author1','year','title','journal','liao','vila','castroDiez')]

#number of papers that overlap across metas
nOverlap.liao<-sum(!is.na(papers.a$liao))
nOverlap.vila<-sum(!is.na(papers.a$vila))
nOverlap.castroDiez<-sum(!is.na(papers.a$castroDiez))
paste('This dataset has', nOverlap.liao, 'papers in common with Liao')
paste(nOverlap.vila, 'papers in common with Vila')
paste(nOverlap.castroDiez, 'papers in common with Castro-Diez')

#make a new column to indicate if the paper is new to this study
papers.a$sourceOverlap<-'PaperInPreviousMeta'
papers.a[is.na(papers.a$liao) & is.na(papers.a$vila) & is.na(papers.a$castroDiez),'sourceOverlap']<-'NewPaper'

#attached the liao, vila, castroDiez columns to the metaDataset if it isn't there already
if(sum(colnames(metaDataset) %in% c('sourceOverlap'))==0){
  temp_indx<-papers.a[,c('paperID','sourceOverlap')]
  metaDataset<-merge(metaDataset, temp_indx, by='paperID')

  #re-write the metaDataset file so that it has the source2 column
  newfilename<-'metaDataset.txt'
  synthdataPath<-file.path(getwd()[1], "DATA", "DATA_SYNTHESIZED")
  write.table(metaDataset, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')
}

```
  
_________________________________________________________________
# 2. Number of papers and observations
```{r papersObs,echo=TRUE, warning=FALSE, message=FALSE}
#how many observations?
paste(length(unique(observations$obsID)), 'observations in the full dataset')
length(unique(metaDataset$obsID)) #these should be the same

#how many observations per paper?
summ.obs <- ddply(observations,~paperID,summarise, numObs=length(paperID))
median(summ.obs$numObs); range(summ.obs$numObs)
pHist_obs<-ggplot(summ.obs, aes(x=numObs)) + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) +
  geom_histogram() + mytheme + 
  ylab('Count') + xlab('Number of observations per paper')
pHist_obs
```

_________________________________________________________________
# 3. Types of observations
```{r obsTypes,echo=TRUE, warning=FALSE, message=FALSE}
tmp <- ddply(metaDataset,~obsID,summarise, 
             ecosyst=unique(ecosystCat),
             stud=unique(studyType),
             nfix=unique(Nfix),
             sourceOverlap=unique(sourceOverlap))
summ.obs.eco<-ddply(tmp, ~ecosyst+sourceOverlap, summarise, numObs=length(obsID))
summ.obs.st<-ddply(tmp, ~stud+sourceOverlap, summarise, numObs=length(obsID))
summ.obs.nfix<-ddply(tmp, ~nfix+sourceOverlap, summarise, numObs=length(obsID))
factorlist<-list(summ.obs.eco, summ.obs.st, summ.obs.nfix)
factortab<-ldply(factorlist)

newfilename<-'numObsTable_categorical.txt'
write.table(factortab, file=paste(figuresPath,newfilename, sep='/'), sep='\t') 

tmp<-ddply(metaDataset,~obsID+traitCat,summarise, 
      InvSpInvArea=unique(InvSpInvArea_cwm),
      NatArea=unique(NatArea_cwm),
      CWMDiff=unique(CWMDiff_cwm),
      sourceOverlap=unique(sourceOverlap))
tmp1<-tmp[!is.na(tmp$traitCat),]
summ.obs.continuous<-ddply(tmp1, ~traitCat+sourceOverlap, summarise, 
                           nObs.Inv=sum(!is.na(InvSpInvArea)),
                           nObs.Ref=sum(!is.na(NatArea)),
                           nObs.Diff=sum(!is.na(CWMDiff)))
summ.obs.continuous
newfilename<-'numObsTable_continuous.txt'
write.table(summ.obs.continuous, file=paste(figuresPath,newfilename, sep='/'), sep='\t') 


```  

_________________________________________________________________
# 4. Plant species statistics 
What is the distribution of invasive species per observation?  Native species? Are certain invasive species over-represented?  
```{r spp,echo=TRUE, warning=FALSE, message=FALSE}
#how many total species x study
paste('There are a total of', dim(species)[1], 'species x study')

#what is the distribution of invasive species per observation?
summ.spp <- ddply(species,~obsID,summarise, 
                  numTotalspp=length(obsID), 
                  numInvspp=sum(spInvasive=='invasive' & spExotic=='exotic' & spFocal=='focal'), 
                  numNonInvspp=sum(spInvasive=='not invasive'),
                  numOthers=numTotalspp-(numInvspp + numNonInvspp))

hist_Inv<-ggplot(summ.spp, aes(x=numInvspp)) + geom_histogram() + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) + 
  mytheme +  
  ylab('Count') + xlab('Number of invasive species per observation')
hist_Inv; median(summ.spp$numInvspp); range(summ.spp$numInvspp)

hist_Nat<-ggplot(summ.spp, aes(x=numNonInvspp)) + geom_histogram() + 
  scale_y_continuous(expand=c(0,0)) + scale_x_continuous(expand=c(0,0)) +  
  mytheme +  
  ylab('Count') + xlab('Number of non-invasive species per observation')
hist_Nat; median(summ.spp$numNonInvspp); range(summ.spp$numNonInvspp)

#number of observations per species
summ.spp.nam <- ddply(species,~spName+spFocal+spExotic,summarise, 
                  numObs=length(obsID), 
                  numPapers=length(unique(paperID)))
spp.many<-summ.spp.nam[which(summ.spp.nam$numObs > 9 & summ.spp.nam$spFocal == 'focal'),] #more than 9 observations
spp.many.o<-orderBy(~-numObs, spp.many)
spp.many.o
positions<-spp.many.o$spName
pHist_spp<-ggplot(spp.many.o, aes(x=spName, y=numObs)) + geom_bar(stat='identity') + 
  scale_y_continuous(expand=c(0,0)) + scale_x_discrete(limits = positions) +
  mytheme +  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  ylab('Number of observations') + xlab('Invasive species')
pHist_spp

newfilename<-'pHist_spp.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*2, height = fig.height*2, res=fig.res)
pHist_spp
dev.off()

#which species appear both as exotic and native species in the dataset? 
summ.spp <- ddply(species,~spName+spExotic, summarise, 
                  numObs=length(obsID),
                  numPapers=length(unique(paperID)))
summ.spp.nam2 <- ddply(summ.spp,~spName,summarise, 
                  numInvNat=length(spExotic)) 
summ.spp.nam2[summ.spp.nam2$numInvNat==2,] # if the length of spInvasive col==2, then there is native and invasive listed
```  

_________________________________________________________________
# 5. Cover data statistics
What percent of observations have measured cover data? 
```{r cover,echo=TRUE, warning=FALSE, message=FALSE}
summ.cov.obs <- ddply(cover,~obsID,summarise, 
                  numMeasured= sum(covQuality=='measured'))
numMeasured.obs<-sum(summ.cov.obs$numMeasured > 0) #number of observations with cover measurement values
numtotal.obs<-length(summ.cov.obs$numMeasured > 0) #total number of observations
cov.obs.perc<-round((numMeasured.obs / (numtotal.obs) ) *100, digits=2)
paste(cov.obs.perc, '% of observations have any cover data at all that was measured in the original paper',collapse='')

#What is the frequency of cover observations for each cover measure type? 
summ.cov <- ddply(cover,~covCat,summarise, 
                  numMeas = length(obsID),
                  numObs=length(unique(obsID)), 
                  numPapers=length(unique(paperID)))
orderBy(~-numMeas, summ.cov)

#What units are commonly reported for each cover measure type?
summ.covUnit <- ddply(cover,~covCat+covUnit,summarise, 
                      numMeas = length(obsID),
                      numObs=length(unique(obsID)), 
                      numPapers=length(unique(paperID)))
COVCAT<-unique(summ.covUnit$covCat)
covUnitList<-list()
i<-0
for(i in 1:length(COVCAT)){
  subdf<-summ.covUnit[summ.covUnit$covCat==COVCAT[i],]
  covUnitList[[as.character(COVCAT[i])]]<-orderBy(~-numMeas, subdf)
}
covUnitList

```  

_________________________________________________________________
# 6. Trait data statistics
```{r traits,echo=TRUE, warning=FALSE, message=FALSE}
# what percent of observations had trait data reported within the original article?
n.ot<-length(unique(traits$obsID)) # number of observations with trait data
n.o<-length(unique(observations$obsID)) # total number of observations
tr.obs.perc<-round((n.ot/n.o) *100, digits=2) # percent of observations with trait data
paste(tr.obs.perc, '% of observations with species-level trait data from the original paper',collapse='')

summ.tr <- ddply(traits,~traitCat,summarise, 
                 numObs = length(unique(obsID)), 
                 numPapers = length(unique(paperID)))
summ.tr.o<-orderBy(~-numObs, summ.tr)
summ.tr.o
positions<-summ.tr.o$traitCat
pBar.tr<-ggplot(summ.tr.o, aes(x=traitCat, y=numObs)) + geom_bar(stat='identity') + 
  scale_y_continuous(expand=c(0,0)) + 
  scale_x_discrete(limits = positions, 
                   labels = c("sp_percN" = "Leaf %N",
                              "sp_cn" = "Leaf C:N", 
                              "sp_litterpercN" = "Litter %N",
                              "sp_littercn" = "Litter C:N")) +
  mytheme +  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  ylab('Number of observations') + xlab('Trait type (species-level)')
pBar.tr

#What units and methods are commonly reported for each measurement? 
summ.traitUnit <- ddply(traits,~traitCat+traitUnit,summarise, 
                   numMeas = length(obsID),
                   numObs=length(unique(obsID)), 
                   numPapers=length(unique(paperID)))
summ.traitUnit
TRAITCAT<-unique(summ.traitUnit$traitCat)
traitUnitList<-list()
i<-0
for(i in 1:length(TRAITCAT)){
  subdf<-summ.traitUnit[summ.traitUnit$traitCat==TRAITCAT[i],]
  traitUnitList[[as.character(TRAITCAT[i])]]<-orderBy(~-numMeas, subdf)
}
traitUnitList
```  

_________________________________________________________________
-- Not Run -- # 7. Soil measurement statistics
```{r meas,echo=TRUE, warning=FALSE, message=FALSE, include=FALSE}
summ.meas <- ddply(measures,~measCat,summarise, numObs=length(unique(obsID)))
summ.meas.o<-orderBy(~-numObs, summ.meas)
summ.meas.o

#What units and methods are commonly reported for each measurement?  
summ.measUnit <- ddply(measures,~measCat+unit,summarise, 
                   numMeas = length(obsID),
                   numObs=length(unique(obsID)))
MEASCAT<-unique(summ.measUnit$measCat)
measUnitList<-list()
i<-0
for(i in 1:length(MEASCAT)){
  subdf<-summ.measUnit[summ.measUnit$measCat==MEASCAT[i],]
  measUnitList[[as.character(MEASCAT[i])]]<-orderBy(~-numMeas, subdf)
}
measUnitList

#re-order measCat levels
metaDataset$measCat <- factor(metaDataset$measCat, levels = measCat_order)

# #re-shape measures so that inv and nat are in the same column temporarily
# tmp<-ddply(metaDataset, ~obsID+measCat, summarize,
#       m1i_logt = unique(m1i_logt),
#       m2i_logt = unique(m2i_logt),
#       measQuality = unique(measQuality))
# tmp$obsID<-as.factor(tmp$obsID)
# m.tmp<-melt(tmp, idcols=c('obsID','measCat','measQuality'))
# m.tmp$invType<-rep(NA,length(dim(m.tmp)[1])) 
# m.tmp[m.tmp$variable == 'm1i_logt','invType']<-'inv'
# m.tmp[m.tmp$variable == 'm2i_logt','invType']<-'ref'
# 
# #Shapiro Test
# # ddply(measures, ~measCat, summarise, 
# #       shapTest=shapiro.test(value)$p.value,
# #       shapTest.Ln=shapiro.test(log(value+1))$p.value)
# #none are normal according to Shapiro test
# 
# # Q-Q plots
# qq<-ggplot(m.tmp, aes(sample=value)) + 
#   facet_wrap(~measCat, scales='free', ncol=3) +
#   stat_qq() + mytheme + ggtitle('QQ Plots of \nstd. measurement values')
# qq
# 
# # Plot Quality Histograms
# #re-order measQuality levels
# m.tmp$measQuality <- factor(m.tmp$measQuality, levels = c('NoAgg.NoConv','NoAgg.Conv','Agg.NoConv','Agg.Conv'))
# 
# pHist_measQual<-ggplot(data=m.tmp, aes(x=value,fill=measQuality)) + mytheme +
#   facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
#   scale_y_continuous(expand = c(0,0)) + 
#   scale_fill_manual(name = "Quality",
#                     labels = c("Agg.Conv"="Aggregated & Converted", 
#                                "Agg.NoConv"="Aggregated",
#                                "NoAgg.Conv"="Converted",
#                                "NoAgg.NoConv"="None"),
#                     values=c("Agg.Conv" = "purple",
#                              "Agg.NoConv" = "red",
#                              "NoAgg.Conv" = "blue",
#                              "NoAgg.NoConv" = "black")) +
#   ylab('Count') + xlab('Standardized measurement value')
# pHist_measQual

```  

_________________________________________________________________
# 8. Effect size statistics
```{r ESmeas,echo=TRUE, warning=FALSE, message=FALSE}
#what is the mean percent change in soil measures from reference to invaded?
#re-shape measures so that inv and nat are in the same column temporarily
tmp<-ddply(metaDataset, ~obsID+measCat, summarize,
      m1i = unique(m1i), #inv
      m2i = unique(m2i)) #ref
tmp$Diff<- tmp$m1i - tmp$m2i
tmp$percDiff<- ((tmp$Diff)/ abs(tmp$m2i))*100 #((inv - ref) / ref)*100
tmp2<-ddply(tmp, ~measCat, summarize,
            meanPercDiff = mean(percDiff, na.rm=T))
tmp2 #mean percent change in soil measures from reference to invaded


#Shapiro Test
# ddply(measures, ~measCat, summarise, 
#       shapTest=shapiro.test(value)$p.value,
#       shapTest.Ln=shapiro.test(log(value+1))$p.value)
#none are normal according to Shapiro test

# Q-Q plots
tmp<-ddply(metaDataset, ~obsID+measCat, summarize,
      yi = unique(yi),
      measQuality = unique(measQuality))
qq<-ggplot(tmp, aes(sample=yi)) + 
  facet_wrap(~measCat, scales='free', ncol=3) +
  stat_qq() + mytheme + ggtitle('QQ Plots of \nEffect sizes')
qq


#Plot Quality Histograms
#re-order measQuality levels
tmp$measQuality <- factor(tmp$measQuality, levels = c('NoAgg.NoConv','NoAgg.Conv','Agg.NoConv','Agg.Conv'))

pHist_ESmeasQual<-ggplot(data=tmp, aes(x=yi,fill=measQuality)) + mytheme +
  facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  scale_y_continuous(expand = c(0,0)) + 
  scale_fill_manual(name = "Quality",
                    labels = c("Agg.Conv"="Aggregated & Converted", 
                               "Agg.NoConv"="Aggregated",
                               "NoAgg.Conv"="Converted",
                               "NoAgg.NoConv"="None"),
                    values=c("Agg.Conv" = "purple",
                             "Agg.NoConv" = "red",
                             "NoAgg.Conv" = "blue",
                             "NoAgg.NoConv" = "black")) +
  ylab('Count') + xlab('Effect size')
pHist_ESmeasQual

```  

_________________________________________________________________
# 9. CWM trait value statistics
```{r cwm,echo=TRUE, warning=FALSE, message=FALSE}

#in each observation, how many invasive and native species are present per invaded and native areas?
#just look at calculated datasets
cwm.calc<-subset(cwm, qualityCWMcalc == 'calculated')
summ.cwm1 <- ddply(cwm.calc,~obsID,summarise,
                  invSp_invArea=unique(n_invSp_invArea),
                  invSp_natArea=unique(n_invSp_natArea),
                  natSp_invArea=unique(n_natSp_invArea),
                  natSp_natArea=unique(n_natSp_natArea))
summ.cwm1$invSp<-summ.cwm1$invSp_invArea + summ.cwm1$invSp_natArea
summ.cwm1$natSp<-summ.cwm1$natSp_invArea + summ.cwm1$natSp_natArea
summ.cwm1$invArea<-summ.cwm1$invSp_invArea + summ.cwm1$natSp_invArea
summ.cwm1$natArea<-summ.cwm1$natSp_natArea + summ.cwm1$invSp_natArea
#what is the distribution of native species in invaded areas
p<-ggplot(summ.cwm1, aes(x=natSp_invArea)) + 
  geom_histogram() + mytheme
p
#which studies have 1 or more native species in an invaded area?
n_studies_natSpInvArea<-length(which(summ.cwm1$natSp_invArea > 0))
n_studies_calcCWM<-dim(summ.cwm1)[1]
perc_studies_natSpInvArea<-round((n_studies_natSpInvArea / n_studies_calcCWM)*100, digits=2)
paste(n_studies_natSpInvArea,'studies have 1 or more non-invasive species in the invaded area, which is ', perc_studies_natSpInvArea,'%')

#which cwms have native species in the invaded area?
#look at the distribution of native species in invaded areas
numberOfSpecies.cwm$number.natSpInvArea<-numberOfSpecies.cwm$number.spInvArea - numberOfSpecies.cwm$number.invSp
weird.obs<-numberOfSpecies.cwm[numberOfSpecies.cwm$number.natSpInvArea<0,'obsID'] #check out these observations
#View(metaDataset[metaDataset$obsID %in% weird.obs,]) #ok it looks like I wasn't able to find trait data for the invasive species
#just exclude those observations for now
numberOfSpecies.cwm1<-subset(numberOfSpecies.cwm, number.natSpInvArea>=0)
p<-ggplot(numberOfSpecies.cwm1, aes(x=number.natSpInvArea)) + 
  facet_wrap(~traitCat)+
  geom_histogram() + mytheme
p
#how many obsIDs x traitCats have 0 native species in the invaded area?
summ.numberOfSp <- ddply(numberOfSpecies.cwm1,~traitCat, summarise,
                         numberObsIDs.natInInvArea=sum(number.natSpInvArea==0),
                         totalObsIDs=sum(!is.na(number.invSp)),
                         perc.sameVals= round((numberObsIDs.natInInvArea/totalObsIDs)*100, digits=2),
                         perc.diffVals=100-perc.sameVals)
summ.numberOfSp
#column name key:
#numberObsIDs.natInInvArea = # of studies with no non-invasive species in the invaded area
#totalObsIDs = # of studies in total that have this type of trait data and are acceptable for inclusion in the meta-analysis
#perc.sameVals = % of studies where the invaded area CWM and invasive species' trait values will be exactly the same
#perc.diffVals = % of studies where the invaded area CWM and invasive species' trait values will be unique

#how many CWMs are calculated vs reported by invType and traitType?
summ.cwm.calc <- ddply(cwm,~traitCat+invType,summarise,
                  nCWMs=sum(!is.na(cwm)),
                  nCWMs_calculated=sum(qualityCWMcalc=='calculated' & !is.na(cwm)),
                  nCWMs_reported=sum(qualityCWMcalc=='reported' & !is.na(cwm)),
                  total.check=sum(nCWMs_calculated,nCWMs_reported))
summ.cwm.calc
newfilename<-'cwm_calc.txt'
write.table(summ.cwm.calc, file=paste(figuresPath,newfilename, sep='/'), sep='\t')


#of the CWMs that are calculated, how many CWMs have each level of quality?
summ.cwm.qual <- ddply(cwm,~traitCat+invType+
                          qualityCWMcalc+ #reported or calculated
                          binMeasCov+bin1spCov+ #cover quality
                          binOrigTr+binTryGS, #trait quality
                       summarise,
                  nCWMs=sum(!is.na(cwm)))
summ.cwm.qual
c.summ<-dcast(summ.cwm.qual, invType+qualityCWMcalc+binMeasCov+bin1spCov+binOrigTr+binTryGS~traitCat, value.var='nCWMs')
newfilename<-'cwm_qual.txt'
write.table(c.summ, file=paste(figuresPath,newfilename, sep='/'), sep='\t')

#by qualRank
summ.cwm.rank <- ddply(cwm,~traitCat+invType+qualRank, summarise,
                  nCWMs=sum(!is.na(cwm)))
summ.cwm.rank
c.summ2<-dcast(summ.cwm.rank, invType+qualRank~traitCat, value.var='nCWMs')
newfilename<-'cwm_qual_rank.txt'
write.table(c.summ2, file=paste(figuresPath,newfilename, sep='/'), sep='\t')

#look at whether the cwm values are normally distributed
#re-shape measures so that inv and nat are in the same column temporarily
tmp<-ddply(metaDataset, ~obsID+traitCat, summarize,
      InvArea_cwm = unique(InvArea_cwm),
      InvSpInvArea_cwm = unique(InvSpInvArea_cwm),
      NatArea_cwm = unique(NatArea_cwm),
      CWMDiff_cwm = unique(CWMDiff_cwm),
      CWMDiff2_cwm = unique(CWMDiff2_cwm),
      InvArea_qualRank = unique(InvArea_qualRank),
      InvSpInvArea_qualRank = unique(InvSpInvArea_qualRank),
      NatArea_qualRank = unique(NatArea_qualRank),
      CWMDiff_qualRank = unique(CWMDiff_qualRank),
      CWMDiff2_qualRank = unique(CWMDiff2_qualRank))
tmp$obsID<-as.factor(tmp$obsID)
m.tmp<-melt(tmp, idcols=c('obsID','traitCat'))
m.tmp$dataType<-rep(NA,length(dim(m.tmp)[1])) #dataType
m.tmp[grepl('_qualRank', m.tmp$variable),'dataType']<-'qualRank'
m.tmp[grepl('_cwm', m.tmp$variable),'dataType']<-'cwm'
m.tmp$invType<-rep(NA,length(dim(m.tmp)[1])) #invType
m.tmp[grepl('InvArea', m.tmp$variable),'invType']<-'InvArea'
m.tmp[grepl('InvSpInvArea', m.tmp$variable),'invType']<-'InvSpInvArea'
m.tmp[grepl('NatArea', m.tmp$variable),'invType']<-'NatArea'
m.tmp[grepl('CWMDiff', m.tmp$variable),'invType']<-'CWMDiff'
m.tmp[grepl('CWMDiff2', m.tmp$variable),'invType']<-'CWMDiff2'
c.tmp<-dcast(m.tmp, obsID+traitCat+invType~dataType)
c.tmp<-c.tmp[!is.na(c.tmp$cwm),]
#View(c.tmp)

# #Shapiro Test
# ddply(cwm, ~traitCat, summarise, 
#       shapTest=shapiro.test(cwm)$p.value,
#       shapTestLn=shapiro.test(log10(cwm))$p.value)
# #none are normal according to Shapiro test

# Q-Q plots
qq<-ggplot(c.tmp, aes(sample=cwm)) + 
  facet_wrap(~traitCat+invType, scales='free', ncol=5) + 
  stat_qq() + mytheme + ggtitle('QQ Plots of \n cwm trait values')
qq


```  

_________________________________________________________________
# 10. Table of articles for supplementary info
```{r papersTable,echo=TRUE, warning=FALSE, message=FALSE}

#subset accepted papers and the relevant columns
#papers.a is from chunk1, above

#add info about the number of observations per paper
nObs<-ddply(observations, ~paperID, summarise,
      nObs=length(obsID))
papers.a1<-merge(papers.a, nObs)

#add info about the number and type of measurements per paper
paperID<-ldply(strsplit(as.character(measures$obsID), '.', fixed=T))[,1]
measures$paperID<-paperID
tmp<-ddply(measures, ~paperID+measCat, summarise,
      nObs=length(obsID))
tmp2<-dcast(tmp, paperID ~ measCat, value.var='nObs', fill=0)
papers.a2<-merge(papers.a1, tmp2)

newfilename<-'paperSummary.txt'
write.table(papers.a2, file=paste(figuresPath,newfilename, sep='/'), sep='\t')




```



_________________________________________________________________
# 11. How much missing species info was there for the observations that needed CWM values calculated?
```{r missingInfo,echo=TRUE, warning=FALSE, message=FALSE}

### 1: Determine which spIDs have cover data, which don't

#Invasive species
#spID that are missing cover data
invSp.cover.na<-cover[is.na(cover$stdmeanInv) & 
                     cover$covInvasive=='invasive' & cover$covFocal=='focal', c('spID')]
invSp.cover.nSp.na<-length(unique(invSp.cover.na[!is.na(invSp.cover.na)]))
#spIDs that have cover data
invSp.cover<-cover[cover$stdmeanInv>0 & !is.na(cover$stdmeanInv) & 
                     cover$covInvasive=='invasive' & cover$covFocal=='focal', c('spID')]

#Invaded area
#spID that are missing cover data
inv.cover.na<-cover[is.na(cover$stdmeanInv),c('spID')]
inv.cover.nSp.na<-length(unique(inv.cover.na[!is.na(inv.cover.na)]))
#spIDs that have cover
inv.cover<-cover[cover$stdmeanInv>0 & !is.na(cover$stdmeanInv),c('spID')]

#Reference area
#spID that are missing cover data
ref.cover.na<-cover[is.na(cover$stdmeanNat), c('spID')]
ref.cover.nSp.na<-length(unique(ref.cover.na[!is.na(ref.cover.na)]))
#spIDs that have cover data
ref.cover<-cover[cover$stdmeanNat>0 & !is.na(cover$stdmeanNat),c('spID')]

#summary
missingCov.tab<-data.frame(communityType=c('InvSp','Inv','Ref'),
                           nSp.missingCover=c(invSp.cover.nSp.na, inv.cover.nSp.na, ref.cover.nSp.na))
missingCov.tab

### 2: Of the spIDs that have cover data, which have trait data?
IdentifyspID.traits<-function(sptrait.df, spID.vec, nSp.missingCoverData){
  
  #calculate the number of unique species entries in the spID.vec
  nSp<-length(unique(spID.vec[!is.na(spID.vec)]))
  
  #identify spIDs in the species x trait dataset
  tmp.spIDs<-sptrait.df[sptrait.df$spID %in% spID.vec,]
  
  #pull out the spIDs that have data for each trait type
  percN.spIDs<-tmp.spIDs[!is.na(tmp.spIDs$mean_percN),c('spID')]
  cn.spIDs<-tmp.spIDs[!is.na(tmp.spIDs$mean_cn),c('spID')]
  litterpercN.spIDs<-tmp.spIDs[!is.na(tmp.spIDs$mean_litterpercN),c('spID')]
  littercn.spIDs<-tmp.spIDs[!is.na(tmp.spIDs$mean_littercn),c('spID')]
  
  listthing<-list(percN=percN.spIDs, cn=cn.spIDs, litterpercN=litterpercN.spIDs, littercn=littercn.spIDs)
  result.tab<-ldply(lapply(listthing, length))
  colnames(result.tab)<-c('traitCat','nSp.withCoverTraitData')
  result.tab$nSp.withCoverData<-rep(nSp, dim(result.tab)[1])
  result.tab$nSp.missingCoverData<-rep(nSp.missingCoverData, dim(result.tab)[1])
  
  return(result.tab)
}

#Invasive species
tmp<-missingCov.tab[missingCov.tab$communityType=='InvSp','nSp.missingCover']
result.invSp<-IdentifyspID.traits(sptrait.df=spIDtraits, 
                            spID.vec=invSp.cover,
                            nSp.missingCoverData=tmp)
#Invaded area
tmp<-missingCov.tab[missingCov.tab$communityType=='Inv','nSp.missingCover']
result.inv<-IdentifyspID.traits(sptrait.df=spIDtraits, 
                            spID.vec=inv.cover,
                            nSp.missingCoverData=tmp)
#Reference area
tmp<-missingCov.tab[missingCov.tab$communityType=='Ref','nSp.missingCover']
result.ref<-IdentifyspID.traits(sptrait.df=spIDtraits, 
                            spID.vec=ref.cover,
                            nSp.missingCoverData=tmp)
#summary
summ.list<-list(invSp=result.invSp, inv=result.inv, ref=result.ref)
summ.tab<-ldply(summ.list)
summ.tab

newfilename<-'traitcoverageSummary.txt'
write.table(summ.tab, file=paste(figuresPath,newfilename, sep='/'), sep='\t') 


```

