---
title: "MIIN Part 3: Calculate effect sizes"
author: "Marissa Lee"
date: "June 1, 2015"
output: pdf_document
---

**Filename: MIIN_3_calcEffectSizes.Rmd**  
**This markdown file does the following tasks:**
1. Clean dataframes: A) Remove observations that do not fit meta-analysis criteria that it must have least 1 focal exotic invasive species AND at least 1 nonfocal species, B) Remove ancillary soil measurements that will not be used in the meta-analysis, C) Simplify ecosystem type factor, D) Identify the N-fixing species, E) Create a character string to identify the invasive species associated with each observation ... then, F) rename all the clean dataframes

2. Calculate invasion effect sizes  

3. Create a composite dataset for analysis. Look at A) dataset structure, B) distribution of invasion effect size values, C) distribution of unit-standardized soil measurement values, and C) distribution of cwm trait values

4. Export dataframes

```{r libraries, echo=TRUE}
knitr::opts_chunk$set(cache=TRUE)

library(plyr)
library(reshape2)
library(ggplot2)
library(metafor)

source('CODE/mytheme.R')

figuresPath<-file.path(getwd()[1], "FIGURES_TABLES", "calcES") #where to put the saved plots
fig.height<-2.5 #inches
fig.width<- 2.5 #inches
fig.res<-300

synthdataPath<-file.path(getwd()[1], "DATA", "DATA_SYNTHESIZED", "calcES") #where to put the clean dataframes

#data synthesized by *MIIN_1_paperData.Rmd*
papers<-read.table("DATA/DATA_SYNTHESIZED/paperData/papers_procd.txt", header=TRUE, sep="\t", quote="") # the quote part is needed to deal with the odd characters inside the doi and notes
observations<-read.table("DATA/DATA_SYNTHESIZED/paperData/observations_procd.txt", header=TRUE, sep="\t") 
cover<-read.table("DATA/DATA_SYNTHESIZED/paperData/cover_procd.txt", header=TRUE, sep="\t") 
species<-read.table("DATA/DATA_SYNTHESIZED/paperData/species_procd.txt", header=TRUE, sep="\t") 
traits<-read.table("DATA/DATA_SYNTHESIZED/paperData/traits_procd.txt", header=TRUE, sep="\t") 
measures<-read.table("DATA/DATA_SYNTHESIZED/paperData/measures_procd.txt", header=TRUE, sep="\t")

#data synthesized by *MIIN_2_cwm.Rmd*
cwm<-read.table("DATA/DATA_SYNTHESIZED/cwm/cwm.txt", header=TRUE, sep="\t")
spIDcover<-read.table("DATA/DATA_SYNTHESIZED/cwm/spIDcover.txt", header=TRUE, sep="\t")
spIDtraits<-read.table("DATA/DATA_SYNTHESIZED/cwm/spIDtraits.txt", header=TRUE, sep="\t")

#read-in the list of Frankia and Rhizobia-associated plant genera
nfixGenera<-read.table("DATA/NfixingPlantGenera.txt", header=TRUE, sep="\t")
legumeGenera<-read.table("DATA/Leguminosae.csv", header=TRUE, sep=',')
```

_________________________________________________________________
# 1. Clean dataframes
1A. Remove observations that do not fit meta-analysis criteria that they must have least 1 focal exotic invasive species AND at least 1 nonfocal species.  Observations will be removed from 'observations' dataframe and the corresponding related data in the following dataframes: cover, species, traits, measures, cwm, papers.
```{r removeObs,echo=TRUE, warning=FALSE, message=FALSE}
summ.spp <- ddply(species,~obsID,summarise, 
                  numTotalspp=length(obsID), 
                  numInvspp=sum(spInvasive=='invasive' & spExotic=='exotic' & spFocal=='focal'), 
                  numNonFocalspp=sum(spFocal=='not focal'))
exclude.1inv<-summ.spp[summ.spp$numInvspp == 0,'obsID']
exclude.1nonfoc<-summ.spp[summ.spp$numNonFocal == 0,'obsID']
exclude.tmp<-c(exclude.1inv,exclude.1nonfoc)
exclude.obsID<-unique(exclude.tmp)

paste('Exclude',length(exclude.obsID), 'observations because there is not at least 1 species that is invasive, exotic, AND focal')

#identify the ok obsIDs
observations1<-observations[!observations$obsID %in% exclude.obsID,]
obsOK<-unique(observations1$obsID)
paste('There are',length(obsOK), 'observations remaining in the dataset that have at least 1 species that is invasive, exotic, AND focal')

#subset the remaining dfs from paperData
cover1<-subset(cover, obsID %in% obsOK)
species1<-subset(species, obsID %in% obsOK)
traits1<-subset(traits, obsID %in% obsOK)
measures1<-subset(measures, obsID %in% obsOK)

#subset the dfs from cwm
cwm1<-subset(cwm, obsID %in% obsOK)
spTOobs<-function(df){ #first, need to convert the spID to an obsID column in these dfs
  tmp<-ldply(strsplit(as.character(df[,'spID']), ".", fixed=T))
  df[,'obsID']<-paste(tmp[,1],tmp[,2], sep=".")
  return(df)
}
spIDcover<-spTOobs(spIDcover)
spIDtraits<-spTOobs(spIDtraits)
spIDcover1<-subset(spIDcover, obsID %in% obsOK)
spIDtraits1<-subset(spIDtraits, obsID %in% obsOK)

#annotate papers dataframe to reflect removal of observations and thus papers
#identify which observations in the exclude list come from papers that had OK'd observations
exclude.p1<-ldply(strsplit(as.character(exclude.obsID), ".", fixed=T))[,1]
include.p1<-ldply(strsplit(as.character(obsOK), ".", fixed=T))[,1]
reject.p<-unique(exclude.p1[!exclude.p1 %in% include.p1]) #if FALSE, then label these paperIDs as rejects
papers[papers$paperID %in% reject.p,'reject']<-'Yes'
newRationale<-'Not at least 1 species that is invasive, exotic, AND focal'
papers$rejectRationale<-factor(papers$rejectRationale, levels=c(levels(papers$rejectRationale),newRationale))
papers[papers$paperID %in% reject.p,'rejectRationale']<-newRationale
papers1<-papers
```
1B. Remove ancillary soil measurements that will not be used in the meta-analysis. 
```{r removeMeas,echo=TRUE, warning=FALSE, message=FALSE}
summ.meas <- ddply(measures1,~measCat,summarise, numObs=length(unique(obsID)))
summ.meas

removeMeasCats<-c('biom','litterbiom','plantcov',
                  'cn','littercn','percN','litterpercN',
                  'microbcn','ph','soilmoi')
paste('Remove these measurement types:', paste(removeMeasCats, collapse=", "))
measOK<-summ.meas[!summ.meas$measCat %in% removeMeasCats,'measCat']

#subset the remaining dfs from paperData
measures2<-subset(measures1, measCat %in% measOK)
measures3 <- droplevels(measures2)
```
1C. Simplify ecosystem type factor
The 'other' category now consists of studies that took place in a dune system, or some combination of forest, grassland, wetland
```{r simpEco,echo=TRUE, warning=FALSE, message=FALSE}
summ.obs.eco <- ddply(observations1,~ecosystCat,summarise, 
                      numObs=length(paperID), 
                      numPapers=length(unique(paperID)))
summ.obs.eco

#limit ecosystem categories to forest, grassland, shrubland, wetland, and other
criteria<-observations1$ecosystCat == 'forest,grassland' | 
  observations1$ecosystCat == 'forest,grassland,wetland' | 
  observations1$ecosystCat == 'dune'
levels(observations1$ecosystCat) <- c(levels(observations1$ecosystCat), "other")
observations1[criteria,'ecosystCat']<-'other'
```
1D. Identify the N-fixing plant species
```{r idNfixers,echo=TRUE, warning=FALSE, message=FALSE}
#pull the unique legume genuses and combine with the full list of Frankia and Rhizobia associated plant genera
LegGenera<-unique(legumeGenera$Genus)
nfixGenera.sub<-nfixGenera[!nfixGenera$plantFamily =='Leguminosae','plantGenera']
nfixGenera.complete<-c(as.character(LegGenera),as.character(nfixGenera.sub))

#select rows in 'species' dataframe based on whether the species' genus name is present in nfixGenera.complete
species1$nfixGenus<-'No' #fill everything in with 'No' first
species1[species1$Genus %in% nfixGenera.complete,'nfixGenus']<-'Yes'
numNfixRows<-dim(species1[species1$Genus %in% nfixGenera.complete,])[1] 
numNonNfixRows<-dim(species1[!species1$Genus %in% nfixGenera.complete,])[1]
paste('There are', numNfixRows, 'and',numNonNfixRows, 'species entries (species unique to each observation) that are N-fixing and non-N-fixing, respectively')

#identify observations based on presence/absence of N-fixer as invasive species
selection<-species1$spInvasive == 'invasive' & species1$spExotic == 'exotic' & species1$spFocal == 'focal' & species1$nfixGenus == 'Yes'
df.selection<-species1[selection,]
NfixObsIDs<-unique(df.selection$obsID)
observations1$InvNfix<-'Non-N-fixing' #fill everthing with 'Non-N-fixing' first
observations1[observations1$obsID %in% NfixObsIDs,'InvNfix']<-'N-fixing'
numNfixRows<-sum(observations1$InvNfix == 'N-fixing')
numNonNfixRows<-sum(observations1$InvNfix != 'N-fixing')
paste('There are', numNfixRows, 'and',numNonNfixRows, 'observations that have N-fixing and non-N-fixing invasive species, respectively')

#identify observations based on % native N-fixing species (not cover)
df.notFocal<-species1[species1$spFocal == 'not focal',]
summ.Nfix <- ddply(df.notFocal,~obsID,summarise,
                     NatnumNfix=sum(nfixGenus=='Yes'), 
                     NatnumNotNfix=sum(nfixGenus=='No'),
                  NatpercNfix=(NatnumNfix/(NatnumNfix + NatnumNotNfix))*100)
summ.Nfix$NatNfix<-'No N-fixers' #fill everthing with 'No N-fixers' first
summ.Nfix[summ.Nfix$NatnumNfix > 0,'NatNfix']<-'N-fixers present'
numNfixRows<-sum(summ.Nfix$NatNfix == 'N-fixers present')
numNonNfixRows<-sum(summ.Nfix$NatNfix != 'N-fixers present')
paste('There are', numNfixRows, 'and',numNonNfixRows, 'observations that have reference areas with N-fixers present and No N-fixers present, respectively')

#create a composite Nfix factor
observations2<-merge(observations1, summ.Nfix, by='obsID')
observations2$Nfix<-paste(observations2$InvNfix, observations2$NatNfix, sep="_")
unique(observations2$Nfix)
observations2$Nfix<-revalue(observations2$Nfix, 
                            c("Non-N-fixing_No N-fixers" = "No N-fixers",
                              "N-fixing_No N-fixers" = "Invasive N-fixers only",
                              "Non-N-fixing_N-fixers present" = "Resident N-fixers only",
                              "N-fixing_N-fixers present" = "Invasive and resident N-fixers"))
```
1E. Create a character string to identify the invasive species associated with each observation  
```{r idInvSp,echo=TRUE, warning=FALSE, message=FALSE}
#create an obsID x invasive species dataframe
species.tmp<-subset(species1, spInvasive=='invasive' & spExotic=='exotic' & spFocal=='focal')
OBSID<-unique(species.tmp$obsID)
bindedrows<-numeric(0)
i<-0
for(i in 1:length(OBSID)){
  invGenera<-paste(species.tmp[species.tmp$obsID == OBSID[i],'Genus'], collapse='_')
  nspecies<-length(species.tmp[species.tmp$obsID == OBSID[i],'Genus'])
  if(nspecies > 2){
    invGenera<-'>2spp'
  }
  row<-data.frame(obsID=OBSID[i], invGenera)
  bindedrows<-rbind(bindedrows,row)
}
species.tmp2<-bindedrows
#View(species.tmp2)

#merge by obsID to add invasive species name to observations table
observations3<-merge(observations2, species.tmp2, by='obsID')
```
1F. Rename all the clean dataframes
```{r rename,echo=TRUE, warning=FALSE, message=FALSE}
papers.c<-papers1
observations.c<-observations3
cover.c<-cover1
species.c<-species1
traits.c<-traits1
measures.c<-measures3
cwm.c<-cwm1
spIDcover.c<-spIDcover1
spIDtraits.c<-spIDtraits1
```

_________________________________________________________________
# 2. Calculate invasion effect sizes and create a composite dataset for analyses (observations, measures, cwm)
To calculate invasion effect sizes, use measurement values that have not been unit-standardized.  Calculate effect sizes using the "standard mean difference" (SMD).
```{r calcES,echo=TRUE, warning=FALSE, message=FALSE}
chooseMeasType<-'nonSTD' #decide whether to use standardized/non-standardized soil measurement values
chooseESType<-'SMD' #decide whether to use ROM or SMD to calculate effect sizes

### Data that will be used ######################################################
#observations.c
#measures.c
#cwm.c

### Calculate measurement ESs ######################################################

#study identifiers
obsID<-measures.c$obsID
measCat<-measures.c$measCat
measQuality<-measures.c$YN

#invader impact measures - standardized units
n1i<-measures.c$inv_n
m1i<-measures.c$inv_mean_std
sd1i<-sqrt(measures.c$inv_var_std)
n2i<-measures.c$nat_n
m2i<-measures.c$nat_mean_std
sd2i<-sqrt(measures.c$nat_var_std)

dat.STD<-data.frame(obsID, measCat, measQuality,
                    n1i, m1i, sd1i, n2i, m2i, sd2i)

#invader impact measures - non-standardized units
m1i<-measures.c$inv_mean
sd1i<-sqrt(measures.c$inv_var)
m2i<-measures.c$nat_mean
sd2i<-sqrt(measures.c$nat_var)

dat.nonSTD<-data.frame(obsID, measCat, measQuality,
                       n1i, m1i, sd1i, n2i, m2i, sd2i)


### Combine the selected measurement ES values with the observation ID modifiers ######################################################
if(chooseMeasType == 'STD'){dat<-dat.STD}
if(chooseMeasType == 'nonSTD'){dat<-dat.nonSTD}

#add obsID factor columns to measures
dat.obs<-merge(dat,observations.c, by='obsID')
#dim(dat);dim(dat.obs) #should more columns, but same number of rows
#colnames(dat.obs) #get rid of unnecessary columns
dat.obs1<-dat.obs[,c('paperID','obsID','measCat',
                 'n1i', 'm1i', 'sd1i', 'n2i', 'm2i', 'sd2i',
                 'measQuality',
                 'ecosystCat','studyType','InvNfix','NatNfix','Nfix','invGenera')]

### Re-organize cwm data and prep for merging ######################################################
#recast cwm so that type of CWM values are in the same row
cwm.tmp<-cwm.c[,c('obsID','traitCat','invType','qualRank','cwm')]
m.cwm.tmp<-melt(cwm.tmp, id.vars=c('obsID', 'traitCat','invType'))
c.cwm.tmp<-dcast(m.cwm.tmp, obsID+traitCat~invType+variable)
#View(c.cwm.tmp)

#calculate the raw difference of invaded and native area cwm trait values
c.cwm.tmp$CWMDiff_cwm<-c.cwm.tmp$InvArea_cwm - c.cwm.tmp$NatArea_cwm

### Combine the selected measurement ES values and obsID info with CWM data ######################################################
#add cwm data to measures
#View(dat.obs1) #each row is a unique obsID x measCat
#View(c.cwm.tmp) #each row is a unique obsID x traitCat
dat.all<-merge(dat.obs1, c.cwm.tmp, by='obsID', all=TRUE)
#dim(dat.all)
#paste(length(unique(dat.obs1$obsID)), 'observations') #check to make sure that observations did not get dropped
#paste(length(unique(dat.all$obsID)), 'observations')

### Calculate the effect sizes ######################################################
dat1 <- escalc(measure=chooseESType, m1i=m1i, sd1i=sd1i, n1i=n1i, m2i=m2i, sd2i=sd2i, n2i=n2i, data=dat.all) 
```

_________________________________________________________________
# 3. Now that we have a composite dataset for analysis. Look at... 
3A. Dataset structure
```{r dataStr, echo=TRUE, warning=FALSE, message=FALSE}
#summarize dataset by unique obsID+measCats so that data is not duplicated (multiple traits per obsID+measCat)
summ<-ddply(dat1, ~obsID+measCat, summarize,
      uniqm1i = length(unique(m1i)),
      uniqm2i = length(unique(m2i)),
      uniqyi = length(unique(yi)),
      total = sum(uniqm1i, uniqm2i,uniqyi))
sum(summ$total != 3) # if 0, then obsID + measCat produces all unique rows
dat1.meas<-ddply(dat1, ~obsID+measCat, summarize,
                 m1i = unique(m1i),
                 m2i = unique(m2i),
                 yi = unique(yi))
#head(dat1.meas) #each row is a unique obsID x measCat

#summarize dataset by unique obsID+traitCats so that data is not duplicated (multiple measures per obsID+traitCat)
summ<-ddply(dat1, ~obsID+traitCat, summarize,
      uniqInvArea = length(unique(InvArea_cwm)),
      uniqInvSpInvArea = length(unique(InvSpInvArea_cwm)),
      uniqNatArea = length(unique(NatArea_cwm)),
      uniqCWMDiff = length(unique(CWMDiff_cwm)),
      total = sum(uniqInvArea, uniqInvSpInvArea,uniqNatArea,uniqCWMDiff))
sum(summ$total != 4) # if 0, then obsID + traitCat produces all unique rows
dat1.tr<-ddply(dat1, ~obsID+traitCat, summarize,
               InvArea = unique(InvArea_cwm),
               InvSpInvArea = unique(InvSpInvArea_cwm),
               NatArea = unique(NatArea_cwm),
               CWMDiff = unique(CWMDiff_cwm))
#head(dat1.tr) #each row is a unique obsID x traitCat

#summarize dataset by unique obsID+traitCats+variable (where variable == c(InvArea, InvSpInvArea, NatArea, CWMDiff)
m.dat1.tr<-melt(dat1.tr, id.vars=c('obsID', 'traitCat')) 
#head(m.dat1.tr) #each row is a unique obsID x traitCat x variable
#sum(is.na(m.dat1.tr$traitCat)) #combination is not fully factorial, so there are NAs here
#sum(is.na(m.dat1.tr$value)) #combination is not fully factorial, so there are NAs here
m.dat1.tr1<-m.dat1.tr[!is.na(m.dat1.tr$value),] #get rid of the NAs
```
3B. Distribution of effect size values
```{r distES, echo=TRUE, warning=FALSE, message=FALSE}
dat1.meas_tmp<-dat1.meas[!is.na(dat1.meas$yi),]

pHist_ES<-ggplot(dat1.meas_tmp, aes(x=yi)) + facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of effect size values')

newfilename<-'pHist_ES.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_ES
dev.off()

#get rid of outliers
#nh
dat1[dat1$measCat=='nh' & dat1$yi > 30 & !is.na(dat1$yi),]
dat1[dat1$measCat=='nh' & dat1$yi > 30 & !is.na(dat1$yi),'yi']<-NA #replace outlier with NA
#no
dat1[dat1$measCat=='no' & dat1$yi > 30 & !is.na(dat1$yi),]
dat1[dat1$measCat=='no' & dat1$yi > 30 & !is.na(dat1$yi),'yi']<-NA #replace outlier with NA
# #ph
# dat1[dat1$measCat=='ph' & dat1$yi > 30 & !is.na(dat1$yi),]
# dat1[dat1$measCat=='ph' & dat1$yi < -30 & !is.na(dat1$yi),]
# dat1[dat1$measCat=='ph' & dat1$yi > 30 & !is.na(dat1$yi),'yi']<-NA #replace outlier with NA
# dat1[dat1$measCat=='ph' & dat1$yi < -30 & !is.na(dat1$yi),'yi']<-NA #replace outlier with NA
#soiln
dat1[dat1$measCat=='soiln' & dat1$yi > 30 & !is.na(dat1$yi),]
dat1[dat1$measCat=='soiln' & dat1$yi > 30 & !is.na(dat1$yi),'yi']<-NA #replace outlier with NA

#update and re-plot
dat1.meas<-ddply(dat1, ~obsID+measCat, summarize,
                 m1i = unique(m1i),
                 m2i = unique(m2i),
                 yi = unique(yi))
pHist_ES_OR<-ggplot(dat1.meas, aes(x=yi)) + facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of effect size values\nOutliers removed')
pHist_ES_OR

paste('Removed outlier effect size values in nh, no, soiln.')
paste('Effect size values look normally-distributed-ish')

newfilename<-'pHist_ES_OR.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_ES_OR
dev.off()
```
3C. Distribution of unit-standardized soil measurement values
```{r distMeas, echo=TRUE, warning=FALSE, message=FALSE}
#m1i (invaded area soil measurements)
pHist_measInv<-ggplot(dat1.meas, aes(x=m1i)) + facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of invaded area soil measurement values')
pHist_measInv
newfilename<-'pHist_measInv.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_measInv
dev.off()

#m2i (reference area soil measurements)
pHist_measRef<-ggplot(dat1.meas, aes(x=m2i)) + facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of reference area soil measurement values')
pHist_measRef
newfilename<-'pHist_measRef.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_measRef
dev.off()

#Log-transform some measurements
# logtMeas<-c('nh','no','toti','soilmoi','som','soiln', 'biom', 'litterbiom','littercn', 'litterpercN','percN')
logtMeas<-c('nh','no','toti','som','soiln')
paste('Log-transform the following soil measurement values to improve normality:',paste(logtMeas, collapse=', '))
nologtMeas<-unique(dat1$measCat)[!unique(dat1$measCat) %in% logtMeas]
SD.logt<-function(meanval, sdval){ #function that corrects the variance values associated with each observation mean value that is log-transformed
  varval<-(sdval)^2
  sd.logt<-sqrt(log10(1+varval/(meanval)^2))
  return(sd.logt)
}
dat1$m1i_logt<-log10(dat1$m1i) #warning message about NaNs is because of negative rate values
dat1$sd1i_logt<-SD.logt(meanval=dat1$m1i, sdval=dat1$sd1i)
dat1$m2i_logt<-log10(dat1$m2i)
dat1$sd2i_logt<-SD.logt(meanval=dat1$m2i, sdval=dat1$sd2i)
#put the non-transformed data back into measures that shouldn't be transformed
dat1[dat1$measCat %in% nologtMeas,'m1i_logt']<-dat1[dat1$measCat %in% nologtMeas,'m1i']
dat1[dat1$measCat %in% nologtMeas,'sd1i_logt']<-dat1[dat1$measCat %in% nologtMeas,'sd1i']
dat1[dat1$measCat %in% nologtMeas,'m2i_logt']<-dat1[dat1$measCat %in% nologtMeas,'m2i']
dat1[dat1$measCat %in% nologtMeas,'sd2i_logt']<-dat1[dat1$measCat %in% nologtMeas,'sd2i']

#update and re-plot
dat1.meas<-ddply(dat1, ~obsID+measCat, summarize,
                 m1i = unique(m1i_logt),
                 m2i = unique(m2i_logt),
                 yi = unique(yi))

pHist_measInv_T<-ggplot(dat1.meas, aes(x=m1i)) + 
  facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of InvArea unit-std soil meas. values\nLog-transformed')
newfilename<-'pHist_measInv_T.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_measInv_T
dev.off()

pHist_measRef_T<-ggplot(dat1.meas, aes(x=m2i)) + 
  facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of NatArea unit-std soil meas. values\nLog-transformed')
newfilename<-'pHist_measRef_T.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_measRef_T
dev.off()

#get rid of outliers
#ammonif
dat1[dat1$measCat=='ammonif' & dat1$m1i_logt > 50 & !is.na(dat1$m1i_logt),]
dat1[dat1$measCat=='ammonif' & dat1$m1i_logt > 50 & !is.na(dat1$m1i_logt),c('m1i_logt','m2i_logt')]<-NA #replace outlier with NA
#dat1[dat1$measCat=='ammonif' & dat1$m1i_logt > 50 & !is.na(dat1$m2i_logt),]


#nitrif
dat1[dat1$measCat=='nitrif' & dat1$m1i_logt > 50 & !is.na(dat1$m1i_logt),]
dat1[dat1$measCat=='nitrif' & dat1$m1i_logt > 50 & !is.na(dat1$m1i_logt),c('m1i_logt','m2i_logt')]<-NA #replace outlier with NA
#dat1[dat1$measCat=='nitrif' & dat1$m1i_logt > 50 & !is.na(dat1$m2i_logt),]

#nminz
dat1[dat1$measCat=='nminz' & dat1$m1i_logt > 100 & !is.na(dat1$m1i_logt),]
dat1[dat1$measCat=='nminz' & dat1$m1i_logt > 100 & !is.na(dat1$m1i_logt),c('m1i_logt','m2i_logt')]<-NA #replace outlier with NA
#dat1[dat1$measCat=='nminz' & dat1$m1i_logt > 100 & !is.na(dat1$m2i_logt),]

#update and re-plot
dat1.meas<-ddply(dat1, ~obsID+measCat, summarize,
                 m1i = unique(m1i_logt),
                 m2i = unique(m2i_logt),
                 yi = unique(yi))

pHist_measInv_T_OR<-ggplot(dat1.meas, aes(x=m1i)) + 
  facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of InvArea unit-std soil meas. values\nLog-transformed and outliers removed')
pHist_measInv_T_OR
newfilename<-'pHist_measInv_T_OR.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_measInv_T_OR
dev.off()

pHist_measRef_T_OR<-ggplot(dat1.meas, aes(x=m2i)) + 
  facet_wrap(~measCat, scales='free', ncol=3) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of NatArea unit-std soil meas. values\nLog-transformed and outliers removed')
pHist_measRef_T_OR
newfilename<-'pHist_measRef_T_OR.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_measRef_T_OR
dev.off()

paste('Removed outlier effect size values in ammonif, nitrif, nminz.')
paste('Most unit-std soil meas. values look normally-distributed after log-transforming some measurement types')
```
3D. Distribution of CWM trait values
```{r distCWM, echo=TRUE, warning=FALSE, message=FALSE}
pHist_cwm<-ggplot(m.dat1.tr1, aes(x=value)) + facet_wrap(~traitCat+variable, scales='free', ncol=4) + geom_histogram() +
  mytheme + scale_y_continuous(expand = c(0,0)) + ggtitle('Histogram of cwm trait values or difference values')
pHist_cwm
newfilename<-'pHist_cwm.png'
png(paste(figuresPath,newfilename, sep='/'), 
    units='in', width = fig.width*3, height = fig.height*6, res=fig.res)
pHist_cwm
dev.off()

paste('No outliers removed at this point, but see MIIN_2_cwm.Rmd')
paste('Most cwm values look normally-distributed - except littercn, probably because there was not very much data')
```

_________________________________________________________________
# 4. Export dataframes
```{r exportData,echo=TRUE, warning=FALSE, message=FALSE}
newfilename<-'papers.txt'
write.table(papers.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t', quote=TRUE, qmethod="double") # the quote part is needed to deal with the odd characters inside the doi and notes

newfilename<-'observations.txt'
write.table(observations.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

newfilename<-'cover.txt'
write.table(cover.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

newfilename<-'species.txt'
write.table(species.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

newfilename<-'traits.txt'
write.table(traits.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

newfilename<-'measures.txt'
write.table(measures.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

newfilename<-'cwm.txt'
write.table(cwm.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

newfilename<-'spIDcover.txt'
write.table(spIDcover.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

newfilename<-'spIDtraits.txt'
write.table(spIDtraits.c, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')

colnames(dat1)
newfilename<-'metaDataset.txt'
write.table(dat1, file=paste(synthdataPath,newfilename, sep='/'), sep='\t')
```




